\documentclass[12pt,a4paper]{report}

% Font configuration - Times New Roman
\usepackage{mathptmx} % Times font for text and math
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Page layout
\usepackage[a4paper, margin=1in]{geometry}

% Essential packages
\usepackage{graphicx} % For including images
\usepackage{hyperref} % For hyperlinks
\usepackage{setspace} % For line spacing
\usepackage{titlesec} % For customizing section titles
\usepackage{tocloft} % For table of contents customization
\usepackage{fancyhdr} % For headers and footers
\usepackage{microtype} % For better typography
\usepackage{xcolor}
\usepackage{listings}

\lstset{
    breaklines=true,
    breakatwhitespace=true
}
% Line spacing (1.5 is common for reports)
\onehalfspacing

% Header and footer configuration
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Title formatting
\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Huge}
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\large\bfseries}{\thesubsection}{1em}{}
% Ensure subsubsections are numbered and appear in the ToC
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={SIWES IT Report},
    pdfpagemode=FullScreen,
}

% Document information
\title{Students Industrial Work Experience Scheme (SIWES)\\
\large IT Report}
\author{Ighalo Genesis Osasenaga}
\date{\today}

\begin{document}

% Title page
\input{titlepage}

% Declaration page
\chapter*{Declaration}
\addcontentsline{toc}{chapter}{Declaration}
I hereby declare that this report is based on my original work during the Students Industrial Work Experience Scheme (SIWES) program. All sources of information have been duly acknowledged.

\vspace{2cm}
\noindent\makebox[2.5in]{\hrulefill}\\
Signature \hspace{2cm} Date

% Abstract
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
This report presents a comprehensive account of the industrial training experience undertaken during the Students Industrial Work Experience Scheme (SIWES). The report covers the activities, skills acquired, challenges encountered, and lessons learned during the training period.

% Acknowledgements
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
I would like to express my sincere gratitude to all those who contributed to the successful completion of my industrial training program. Special thanks to my supervisors, colleagues, and family for their support and guidance throughout this period.

% Table of contents
\tableofcontents
\newpage

% List of figures and tables
\input{list_of_tables_and_figures}
\newpage

% Abbreviations and keywords
\input{abbreviations}
\newpage

% Main content
\input{chapter1}
\input{chapter2}
\input{chapter3}
\input{chapter4}

% References (if needed)
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{References}

\bibitem{example}
Author Name, \textit{Title of Work}, Publisher, Year.

\end{thebibliography}

% Appendices (if needed)
\appendix
\chapter{Additional Documents}
Include any additional documents, certificates, or supplementary materials here.

\end{document}
